---
title: "Manuscript_Draft"
author: "Beating Bu"
date: "1 December 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## **Markdown Draft for the model masuscript**

This markdown is a collaborative draft for the production of a manuscript about the joint possum-mosquito SDM.

The current collaborating authors (in no particular order) are: Saras Windecker, Shona Elliot- Kerr 

Other acknowledgements should be made to: [add any people who collaborated but don't want authorship]


The aim of the file is to collect points for the , a target journal 

## Introduction notes

Add intro notes here

## Method notes
```{r data read, echo= FALSE}
mossie.dat <- read.csv("mossie_SDM/data_mossie/final.mosquito.data.csv")
```

**Mosquito Methods**
[information about collection methods]
Egg trap data was collected by Veronique Paris, Alys Young (and others?). The traps were set out for 7 days across Greater Melbournce with two traps per gps location. The adult data used [CO2 traps]

